The hydra and the rooster

### 2020-08-20 latex/chapter-hydras.tex
new exercise
typo corrections in *.tex

\pagebreak
\vspace{4pt}\emph{From Module\href{../src/html/hydras.Hydra.Hydra_Definitions.html}{Hydra.Hydra\_Definitions}}

@@

The reader is encouraged to look at all the intermediary subgoals of this example.
\emph{Please consider also exercise~\vref{exo:interactive-battle}.}

@@

The proof we are going to develop has exactly the same structure as in Section~\ref{sect:omega:case}

previous one. Nevertheless, the proof of technical  lemmas is a little more complex, due to 
 the structure of the lexicographic order on $\mathbb{N}\times\mathbb{N}$. 
Consider for instance that there exists an infinite number of pairs between
$(1,0)$ and $(2,0)$.

>>>>

\vspace{4pt}\emph{From Module\href{../src/html/hydras.Hydra.Hydra_Definitions.html}{Hydra.Hydra\_Definitions}}

@@

The reader is encouraged to look at all the successive subgoals of this example.
\emph{Please consider also exercise~\vref{exo:interactive-battle}.}

@@

The proof we are going to develop has exactly the same structure as in Section~\ref{omega-case}.
 Nevertheless, the proof of technical  lemmas is a little more complex, due to 
 the structure of the lexicographic order on $\mathbb{N}\times\mathbb{N}$. 
Consider for instance that there exists an infinite number of pairs between
$(1,0)$ and $(2,0)$.

### 2020-08-20 latex/chapter-ks.tex
proof simplification in L_alpha
typo corrections in *.tex

\section{Accessibility inside \texorpdfstring{$\epsilon_0$}{epsilon0} : Paths}
\index{Maths!Accessibility inside epsilon0}

@@

\index{Predicates!path\_to}

@@

\item Otherwise,  $\beta < \gamma$.  Let us consider  $\delta=\canonseq{\gamma}{n+l+2}$.
By applying several times lemma \texttt{Cor12},  one converts  every path of Fig~\ref{fig:belle-preuve-2} into
 a $n+l+1$-path  (see figure~\ref{fig:belle-preuve-3}).

But $\gamma$ is on the $n+l+1$-path from $\alpha$ to $\beta$.
As shown by figure~\vref{fig:fin-belle-preuve}), the ordinal $\delta$, reachable from
$\gamma$ in one single step,  must be greater than or equal to $\beta$, which contradicts our  hypothesis $\beta < \gamma$.

\end{itemize}
 The only remaining case is  $\beta=\gamma$, thus we have got a standard path
from $\alpha$ to $\beta$.

End Constant_to_standard_Proof.

Lemma constant_to_standard_path 
  (alpha beta : T1) (i : nat):
  nf alpha -> const_pathS i alpha beta -> zero  o< alpha ->
  {j:nat | standard_path (S i) alpha j beta}.
\end{Coqsrc}

@@

@@

Since $m(\texttt{big\_h })< \mu$, there exists a standard path from $\mu$ to
$m(\texttt{big\_h})$, hence a   standard battle from $\iota(\mu)$  to
$\iota(m(\texttt{big\_h}))$,  i.e. from \texttt{big\_h} to \texttt{small\_h}.

>>>>

\section{Accessibility inside \texorpdfstring{$\epsilon_0$}{epsilon0} : Paths}
\index{Maths!Accessibility inside epsilon0}
\label{sect:pathes-intro}

@@

\index{Predicates!path\_to}
\label{sect:path-to-def}

@@

\item Otherwise,  $\beta < \gamma$.  Let us consider  $\delta=\canonseq{\gamma}{n+l+1}$.
By applying several times lemma \texttt{Cor12},  one converts  every path of Fig~\ref{fig:belle-preuve-2} into
 a $n+l+1$-path  (see figure~\ref{fig:belle-preuve-3}).

But $\gamma$ is on the $n+l+1$-path from $\alpha$ to $\beta$.
As shown by figure~\vref{fig:fin-belle-preuve}, the ordinal $\delta$, reachable from
$\gamma$ in one single step,  must be greater than or equal to $\beta$, which contradicts our  hypothesis $\beta < \gamma$.

@@

\end{itemize}
 The only possible case is  thus $\beta=\gamma$, so we have got a standard path  from $\alpha$ to $\beta$.

End Constant_to_standard_Proof.
\end{Coqsrc}

Here is the full statement of the conversion from constant to standard paths.

\begin{Coqsrc}
Lemma constant_to_standard_path 
  (alpha beta : T1) (i : nat):
  nf alpha -> const_pathS i alpha beta -> zero  o< alpha ->
  {j:nat | standard_path (S i) alpha j beta}.
\end{Coqsrc}

@@

Since $m(\texttt{big\_h})< \mu$, there exists a standard path from $\mu$ to
$m(\texttt{big\_h})$, hence a   standard battle from $\iota(\mu)$  to
$\iota(m(\texttt{big\_h}))$,  i.e. from \texttt{big\_h} to \texttt{small\_h}.
